### 2025-01-24 our_article/MCM_article/article_file.tex
论文修改

\documentclass{HZNUMCM}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{subcaption}
\definecolor{customcolor}{HTML}{429938}

\setControlNumber{888888}
\setContestType{MCM}
\setProblemLetter{A}
\setPaperTitle{Our Article}

@@

        \textbf{Explanation}: The climate of Southeast Asia is simple, with only two seasons—rainy and dry. Additionally, the temperature variation within a year is minimal.
        \item \textbf{Planting Pattern Assumption}: The model assumes that two crops of rice are planted each year in the farmland.

@@

  \section{Models}

>>>>

\documentclass{HZNUMCM}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{float}
\definecolor{customcolor}{HTML}{429938}

\setControlNumber{2511940}
\setContestType{MCM}
\setProblemLetter{E}
\setPaperTitle{Our Article}

@@

        \textbf{Explanation}: The climate of Southeast Asia is simple, with only two seasons—rainy and dry. Additionally, as is shown in \figurename~\ref{fig:Temperature},the temperature variation within a year is minimal,which leads to trivial effect on the ecosystem.Consequently,temperature can be considered as a constant.
        \begin{figure}[H]
          \centering
          \includegraphics[width=\linewidth]{images/AverTemper.png}
          \caption{Mean Temperature from 1991 to 2020 in Southeast Asia}
          \label{fig:Temperature}
        \end{figure}
        \item \textbf{Planting Pattern Assumption}: The model assumes that two crops of rice are planted each year in the farmland.

@@

  \section{Models}
        % figure
    \begin{figure}[ht]
      \centering
      \includegraphics[width=0.5\linewidth]{images/energy_flow.png} % 替换为你的第一张图片路径
      \caption{Energy Flow}
      \label{fig:EnergyFlow}
    \end{figure}
